Shannon diversity

### 2021-02-22 analysis/rev_prototyping/additional_metrics_results.Rmd
prelim stuff

---
title: "Prop off"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
---

@@

all_di <- read.csv(here::here("analysis", "rev_prototyping", "mcdb_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1) %>%
  mutate(prop_off_sig_mean = mean_prop_off_actual >= prop_off_sim_95,
         prop_off_sig_5pc = prop_off_actual_5 >= prop_off_sim_95)

@@

@@

ggplot(filter(all_di, n_po_comparisons > 20), aes(mean_po_comparison_percentile)) +
  geom_histogram() +
  facet_wrap(vars(singletons), scales = "free_y")

ggplot(filter(all_di, n_po_comparisons > 20), aes(n_po_comparisons)) +
  geom_histogram()

all_di %>% group_by(singletons) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))

@@

>>>>

---
title: "Other metrics"
author: Renata Diaz
date: "`r Sys.Date()`"
output: 
    github_document:
       df_print: kable
       toc: true

---

@@

all_di <- read.csv(here::here("analysis", "rev_prototyping", "all_di.csv"))

all_di <- all_di %>%
  filter(s0 > 1,
         s0 != n0,
         n0 != s0 + 1)

@@

## Proportion off

@@

ggplot(filter(all_di), aes(mean_po_comparison_percentile)) +
  geom_histogram() +
  facet_wrap(vars(dat, singletons), scales = "free_y")

all_di %>% group_by(singletons, dat) %>% summarize(po_sig = mean(mean_po_comparison_percentile > 95))

@@

ggplot(all_di, aes(mean_po_comparison_sims, mean_po_comparison, color = mean_po_comparison_percentile > 95)) +
  geom_point(alpha = .3) +
  facet_wrap(vars(dat, singletons))

ggplot(all_di, aes(mean_po_comparison - mean_po_comparison_sims, color = mean_po_comparison_percentile > 95)) +
  geom_histogram(alpha = .3) +
  facet_wrap(vars(dat, singletons))

## Number of singletons

## Shannon diversity

### 2021-02-22 analysis/rev_prototyping/old/prop_off.Rmd
prelim stuff

@@

all_di <- all_di %>%
  mutate(prop_singles_actual = nsingletons / s0,
         sim_prop_singles_95 = nsingletons_95 / s0,
         sim_prop_singles_mean = nsingletons_mean / s0) %>%
  mutate(
            actual_minus_95_prop = prop_singles_actual - sim_prop_singles_95)

>>>>

ggplot(all_di, aes(skew_percentile > 95, mean_prop_off_actual)) +
  geom_boxplot() +
  facet_wrap(vars(dat, singletons))

ggplot(all_di, aes(simpson_percentile < 5, mean_prop_off_actual)) +
  geom_boxplot() +
  facet_wrap(vars(dat, singletons))

ggplot(all_di, aes(shannon_percentile < 5, mean_prop_off_actual)) +
  geom_boxplot() +
  facet_wrap(vars(dat, singletons))
```

```{r}

@@
